Mass and occupation fraction of dark matter halos hosting Lyman-$\alpha$ emitters at $z\sim 3$

### 2013-11-13 paper/ms.tex
introduction rewritten

Some theoretical attempts to solve this problem using an  ab-initio
approach. They start from the DM halo population to infer the
intrinsic star formation rates and \ly a luminosities. From these
values they estimate the amount of \ly photons that
escape each galaxy and compute the observed luminosity for each
galaxy. These models can predict different observables including: the
luminosity function, correlation function and the equivalent width
distributions. Such modelling has been implemented in semi-analytic
models \citep{Garel2012,   Orsi2012, Solre2012} and  full N-body
hydrodynamical simulations \citep{Laursen2007, Dayal2009,
  ForeroRomero2011, Yajima2012}.

@@

Another approach to infer the typical DM halo mass of halos hosting
LAEs is based on the clustering information. This uses the fact that in cold
dark matter cosmologies the spatial clustering of galaxies on large
scales is entirely dictated by the halo distribution
\citep{Colberg00}, which in turn has a strong dependence on halo
mass. Using measurements of the angular correlation function of LAEs,
observers have put constraints on the typical mass and occupation
fraction of the putative halos hosting these galaxies
\citep{Hayashino2004,Gawiser07,Nilsson2007,Ouchi2010}. In this
studies the observations were done on single fields of $\sim 1$
deg$^{2}$ and the conclusions derived on the halo host mass from
clustering information do not delve to deeply into the impact of
cosmic variance.

{\bf \cite{Soler2012} has derived the median mass of $z=0$ the $z=3.1$ LAE 
descendat.  In order to construct their  LAE mock catalogs 
they impose their model to reproduced, whitin the observational errors,
 the number density  as well as  the minimal and median mass reported 
 by \cite{Gawiser07} that has been derived from observations
 over one single field. }

Recently \cite{Yamada2012} observed a wide area a bit more than ten
times the sky area covered so far by individual campaigns. The
observations were done with the same instrument and same criteria to
reduce the observational data and produce LAE catalogs. This large
data-set allows us to make the first study on the expected cosmic
variance effects in LAEs at $z=3.1$ and its impact on the
determination of the halo mass and occupation fraction.

In this \documentname we implement a method to populate the DM halos
in cosmological simulations with LAEs that bypasses all the
uncertainty involved in the estimation of star formation rates and \ly escape
fraction. The model only considers whether a DM can host a
detectable LAE or not without predicting a \ly  luminosity. Once the
mock catalogs are constructed  we proceed with a direct comparison
against the statistics on the number density distribution derived from
 the observations over the 12 fields of \cite{Yamada2012}. This allows us 
to find the preferred mass range of DM halos hosting these galaxies
and its occupation fraction.

This \documentname is structured as follows. In the next section we present
the simulation and model used to produce the mock catalogs and the criteria
we use to compare them against observations. In \S \ref{sec:results} we
present the main results for the halo mass and occupation fraction. We
continue with a discussion of these results under the light of other
observational and theoretical results. Finally, we present our
conclusions in \S \ref{sec:conclusions}.

>>>>

Some theoretical attempts to solve this problem using an  ab-initio
approach. They start from the DM halo population to infer the
intrinsic star formation rates and \ly a luminosities. From these
values they estimate the amount of \ly photons that
escape each galaxy and compute the observed luminosity for each
galaxy. These models can predict different observables including: the
luminosity function, correlation function and the equivalent width
distributions. Such modelling has been implemented in semi-analytic
models \citep{Garel2012,Orsi2012, Solre2012} and  full N-body
hydrodynamical simulations \citep{Laursen2007, Dayal2009,
  ForeroRomero2011, Yajima2012}.

@@

A different approach to infer the typical mass of halos hosting
LAEs is based on clustering information. This method uses the fact
that in CDM cosmologies the spatial clustering of galaxies on large
scales is entirely dictated by the halo distribution
\citep{Colberg00}, which in turn has a strong dependence on halo 
mass. Using measurements of the angular correlation function of LAEs,
observers have put constraints on the typical mass and occupation
fraction of the putative halos hosting these galaxies
\citep{Hayashino2004,Gawiser07,Nilsson2007,Ouchi2010}. In these
studies the observations are done on fields of $\sim 1$ deg$^{2}$ and
the conclusions derived on the halo host mass do not delve too deeply
into the possible impact of cosmic variance.

Recently \cite{Yamada2012} observed a wide area of $2.4$ deg$^{2}$
under homogeneous instrumental and data reduction conditions. This data
set is constructed from 12 different sub-fields. This large and
homogeneous data-set allows us to use clustering statistics and cosmic
variance to constraint the mass and occupation fraction of halos hosting
LAEs.

Our method first populates DM halos in cosmological simulations with
LAEs. We only consider whether a DM can host a detectable LAE or not
without predicting a \ly  luminosity. This is constructed to bypass
all the physical uncertainties involved in the estimation of observed
\ly luminosities.  Once we have the mock LAE catalogs, we compare them
against the statistics on the number density distribution derived from the
observations over the 12 fields of \cite{Yamada2012}. Additionally, we
use measurements of the angular correlation function to improve these
constraints. This method allows us to find the preferred mass range of
DM halos hosting these galaxies and its occupation fraction.

This \documentname is structured as follows. In the next section we present
the simulation and the model used to produce the mock catalogs. We
also list the criteria used to compare the mocks against
observations. In \S \ref{sec:results} we present the main results for
the halo mass and occupation fraction. We continue with a discussion
of these results under the light of other observational and
theoretical results. Finally, we present our conclusions in \S
\ref{sec:conclusions}.
